---
title       : Iris Analysis And Prediction
subtitle    : Prediction of Species using glmnet
author      : Roshan Shetty
job         : Intern at SAP, Budding Data Scientist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Motivation

1. Iris features are a good indicator of species
2. Dataset is available which can be used for prediction
3. Helps anyone interested to collect new data and make predictions

--- .class #id 

## Analysis

Iris summary gives indication of range of inputs to be used
```{r}
summary(iris)
```

---

## Model

1. A glmnet model is used for predicting the species of the data
```{r echo=TRUE}
cv.fit <- cv.glmnet(as.matrix(iris[,-5]), 
                    iris[,5], alpha=0.8, 
                    family="multinomial")
```

2. The predict function helps in predicting new values
```{r echo=TRUE}
  species <- predict(cv.fit, 
                        newx=as.matrix(test),
                        type="class")
```

--- 

## Application UI
The following UI will be visible to the user. Note that this does not run the prediction here.
```{r opts.label = 'shiny'}
slidifyUI(
    #headerPanel("IRIS data Prediction Assignment using Shiny"),
    sidebarPanel(      
      #textInput(inputId="Sepal Length", label="Input Text1"),
      #textInput(inputId="text2", label="Input Text2"),
      numericInput(inputId='Sepal.Length',label='Sepal Length',value=5,min=4.3, max=7.9, step=0.1),
      numericInput(inputId='Sepal.Width',label='Sepal Width',value=2.5,min=2, max=4.4, step=0.1),
      numericInput(inputId='Petal.Length',label='Petal Length',value=2,min=1, max=6.9, step=0.1),
      numericInput(inputId='Petal.Width',label='Petal Width',value=1,min=0.1, max=2.5, step=0.1),
      submitButton('Submit')
      #actionButton("goButton","Go!")
    ),
    mainPanel(
      h3('Results of prediction'),
      h4('You entered'),
      p('Sepal Length'),
      textOutput('sepalLen'),
      p('Sepal Width'),
      textOutput('sepalWid'),
      p('Petal Length'),
      textOutput('petalLen'),
      p('Petal Width'),
      textOutput('petalWid'),
      #p('Inside text, but non-reactive'),
      #textOutput('text5'),            
      h4('Which results in a prediction of '),
      textOutput("Species")
      )   
    )

```


